---
title: "EMPTY_Experimental_Data_Analysis"
author: "PSYC300"
format: docx
editor: visual
---

## The Paper

Kampfer, K., Leischnig, A., Ivens, B. S., & Spence, C. (2017).
Touch-flavor transference: Assessing the effect of packaging weight on
gustatory evaluations, desire for food and beverages, and willingness to
pay. *PloS one*, 12(10), e0186121.

Companies influence consumers in subtle ways when trying to persuade
them to purchase a product. Things like package shape, material, use of
color, and font can change consumer perception of a product's quality.
One such factor is package weight. These researchers proposed that the
weight of a package would influence how willing one would be to purchase
that product.

Participants were measured on a battery of constructs including
perceptions of flavor, willingness to purchase, biological sex, and age.
These data are a subset of the original data collected in the study. The
analyses we do will not necessarily emulate the ones in the paper.

Understanding potential reasons why one may purchase a product can
empower consumers to not fall for tricks that manufacturers play like
package weight.

## The Variables

**WEIGHT:** Whether the participates ate chocolate from a weighted (2)
wrapper or not (1).

**FLAV_INT:** A self-report measure of the perceived  flavor intensity
of the chocolate. One item on a scale of 1-7.

**PURCHASE:** An open-ended question coded on a scale of 1-10, where
larger values indicate a greater willingness to purchase the product.

**SEX:** The participant's biological sex (1 = Male, 2 = Female).

**AGE:** The participant's age (standardized).

For all constructs, higher values = greater levels of construct.

## The Analysis

We are going to fit a model to the data with their experimental group
(heavy/light wrapper; WEIGHT) as the predictor and their purchasing
likelihood as the outcome (MCIVIL).

### Load the Required Packages

We need to read in [**ggplot2**]{.underline} and
[**jtools**]{.underline}.

```{r}

```

### Read in the Data

If you're working on Jupyter, this is in the same folder as the file so
you won't need the file path.

```{r}

```

### Generate Descriptive Statistics

Use the summary command.

```{r}

```

### Visualize the Data

What visualization would be appropriate for a dichotomous predictor and
continuous outcome?

**Answer:**

```{r}
ggplot(data = choc, aes(x = as.factor(weight), y = purchase)) +
  geom_boxplot() + 
  labs(x = "Condition (1 = Unweighted Wrapper, 2 = Weighted Wrapper", y = "Purchasing Intent") + 
  jtools::theme_apa()
```

How do the assumptions look?

-   Linearity:

-   Homogeneity of variance:

-   Normality of residuals: If you want, you can check this in the
    "Model" section using the command hist(resid(model_name))

### Fit the Model to the Data

What test should you run? (Note: The command in R is the same.)

**Answer:**

```{r}
# run the analysis between the weight and purchase variables

```

What are the results? Try in APA format.

**Answer:**

### Exploratory Data Analysis

Run the code below if you want to explore the relationship between other
variables in the dataset. You can also test out other relationships
you're interested in! (Or just ignore; the code below will render just
fine.)

```{r}
ggplot(data = choc, aes(x = as.factor(weight), y = flav_eval)) +
  geom_boxplot() + 
  labs(x = "Flavor Evaluation", y = "Flavor Intensity") + 
  jtools::theme_apa()
#t.test()

# exploratory data analysis
ggplot(data = choc, aes(x = flav_eval, y = purchase)) +
  geom_point() + 
  labs(x = "Flavor Evaluation", y = "Purchasing Intent") + 
  jtools::theme_apa()
cor.test(choc$flav_eval, choc$flav_int)
```

## End of script
