---
title: "R Training Session"
author: Jacob Coutts
format: docx
editor: visual
---

-   Use this to practice reading in .csv files and manipulating the data.

## Step 1: Read in the data.

First, let's read in the data so we can practice running some analyses. Either download the data from Jupyter/lab page and upload it or just run the code if it's all in Jupyter.

```{r}
NAME_YOUR_DATA_FRAME_YOUR_NAME_AND_USE_THIS_FROM_HERE_ON_OUT <- read.table("REPLACE_THIS_WITH_THE_NAME_OF_THE_FILE.csv",sep=",",header=TRUE)
```

## Step 2: Change the names of the columns in R.

There are four columns in the data, the last two are named *X* and *Y*. (It looks like they got unnamed somehow!) Please change these to depression_TOT and optimism_TOT, respectively, so we know what we're working with.

```{r}
names(DATAFRAMENAME) # will give you the column names of the data frame
names(DATAFRAMENAME) <- c("Check","Test") # will change the names of the first two columns to 1 and 2. We don't want that, so don't run this code. 
names(DATAFRAMENAME)[3:4] <- c() # what will this do and why?? 
```

## Step 3: Explore the data.

-   Now, let's explore the data with the summary command.
-   Calculate the mean and standard deviation of depression_TOT and optimism_TOT. You should get 2.90 (0.622) and 20.957 (12.02), respectively.
-   How many observations are in the dataset? How can you tell this? (Hint, look for a command that shows you the number of ROWS. That's two hints in one.)

```{r}
# modify this to fit your problem
summary()
```

## Step 4: Analyzing data.

I want to conduct a few different analyses on these data.

-   First, compute the correlation between depression_TOT and optimism_TOT. You should use the cor.test() function to do this. (Hint: The correlation is negative and starts with a -0.5...) What is the p-value? Is this statistically significant?

-   Now, I want to compare the scores of men and women on depression in the sample. We can use the gender variable as a basis for this. 0 means the respondent identified as a man and 1 means the respondent identified as a woman. (No other genders were observed in this sample.) How can I do this? (Hint: t-...?) What is the *p*-value? Is this statistically significant? (Hint: the *p*-value for this test starts as .01...)

```{r}
# to compute correlation between two variables
cor.test()
# to compare two groups on another variable
t.test()
```

## Step 5: Visualizing the data.

Now, let's use ggplot to bring it all together.

-   How do we visualize the relationship between two numeric variables? Which plot should we use?

-   What about for the relationship between gender and depression?

```{r}
# for numeric x and y 
ggplot(REPLACE_WITH_NAME_OF_YOUR_DATA, aes(x=REPLACE_WITH_NAME_OF_YOUR_X, y=REPLACE_WITH_NAME_OF_YOUR_Y)) + 
  geom_point() + 
  geom_jitter() + 
  ggtitle("GIVE AN INFORMATIVE TITLE.") + 
  labs(y="REPLACE WITH OUTCOME NAME", x = "REPLACE WITH PREDICTOR NAME")

# for dichotomous x and numeric y
ggplot(REPLACE_WITH_NAME_OF_YOUR_DATA, aes(x=REPLACE_WITH_NAME_OF_YOUR_X, y=REPLACE_WITH_NAME_OF_YOUR_Y)) + 
  geom_point() + 
  geom_jitter() + 
  ggtitle("GIVE AN INFORMATIVE TITLE.") + 
  labs(y="REPLACE WITH OUTCOME NAME", x = "REPLACE WITH PREDICTOR NAME")
```

### End of script

Render as a .docx or .html and upload to the progress report!
